---
title: "Results from SEIR model parameter sweep"
author: "Microsim Team"
date: '`r format(Sys.time(), "%B %d, %Y") `'
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float: true
    toc_depth: 5
    code_folding: show
editor_options:
  chunk_output_type: console
---

<style>
  html, body { font-size: 14px; }
  p { margin-bottom: 18px; }
  h1 { margin-top: 30px; font-size: 1.75rem; }
  h1.title {font-size: 2rem;  }
  h2 { font-size: 1.35rem; margin-top: 30px; }
  h3 { font-size: 1.15rem; margin-top: 30px; }
  h4 { font-size: 1.05rem; margin-top: 30px; }
  h4.date { margin-top: 0; margin-bottom: 3rem; }
  p.caption { margin-top: 2rem; }
  img { width: 100%; height: auto; }
  blockquote { border-left: 5px solid #337ab7; border-bottom: 1px solid #efefef; font-weight: normal; font-size: 1rem; }
  .dataTables_filter, .dataTables_length {font-weight: normal; }
  div.main-container { width: 100% !important; max-width: 100% !important; margin-left: auto; margin-right: auto; }
  td.dt-top { vertical-align: top; }
  .level3 h3, .level4 h4 { color: #337ab7; font-weight: bold; }
  .level4 h4 { margin-top: 96px;}
  li > img { margin-top: 24px; margin-bottom: 24px; }
</style>

<img src="https://www.statcan.gc.ca/wet-boew4b/assets/sig-blk-en.svg" style = "max-width: 300px; height: auto; margin-bottom: 24px;" alt="logo">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, dpi = 300)
```

> Note: these 300 scenarios were run with half.range = 0.4 (April 20th sheet).

# Load packages to extend base R

```{r}
# Define packages that will be used to extend base R
package_names <- c("janitor","readxl","dplyr","deSolve","tidyr","ggplot2", "ggpubr", "tidyverse", "shiny", "shinycssloaders", "DT", "scales", "plotly", "matrixcalc") 

# Install any packages that do not exist
install_packages <- lapply(package_names, FUN = function(x) if(! require(x, character.only = TRUE)) install.packages(x))

# Load the packages
load_packages <- lapply(package_names, require, character.only = TRUE)
```

# Import summary data

```{r}
outcomes.summary.df <- read.csv("c:/users/joel/google drive/github/seir/claude_v8(2)/300 scenarios - 0.4 half range, April 20 sheet.csv", stringsAsFactors = FALSE)
```

# Wrangle data

```{r}
# Create a scenario grouping variable (factor)
lookup <- tibble(long = unique(outcomes.summary.df$etiquette), short = 1:length(unique(outcomes.summary.df$etiquette)))

outcomes.summary.df$scenario <- factor(sapply(outcomes.summary.df$etiquette, function(x) lookup$short[x == lookup$long]))
```

# Scatter plots
## Time (day number) by peak incidence

```{r}
# Print scatter plot
plot_title <- paste0("Time (day number) by peak incidence, based on ", nrow(outcomes.summary.df)," scenarios")
x_label <- "Peak incidence (individuals per day)"
y_label <- "Time (day number)"
point_size <- 0.5
element_text_size <- 12
plot_width <- 900
plot_height <- 614
ggplotly(ggplot(outcomes.summary.df, aes(x = maxI, y = maxI.time)) +
    geom_point(aes(color = scenario), size = point_size) +
    ggtitle(plot_title) +
    xlab(x_label) +
    ylab(y_label) +
    theme_minimal() +
    theme(
       plot.title = element_text(size = element_text_size),
       axis.title.x = element_text(size = element_text_size),
       axis.title.y = element_text(size = element_text_size),
       legend.text = element_text(size = element_text_size),
       legend.title = element_blank()
  ), width = plot_width, height = plot_height)
```

## Time (day number) of peak incidence by Cgg multiplier

```{r}
# Print scatter plot
plot_title <- paste0("Time (day number) of peak incidence by Cgg multiplier, based on ", nrow(outcomes.summary.df)," scenarios")
x_label <- "Cgg multiplier"
ggplotly(ggplot(outcomes.summary.df, aes(x = Cgg.multiplier, y = maxI.time)) +
    geom_point(aes(color = scenario), size = point_size) +
    ggtitle(plot_title) +
    xlab(x_label) +
    ylab(y_label) +
    theme_minimal() +
    theme(
       plot.title = element_text(size = element_text_size),
       axis.title.x = element_text(size = element_text_size),
       axis.title.y = element_text(size = element_text_size),
       legend.text = element_text(size = element_text_size),
       legend.title = element_blank()
  ), width = plot_width, height = plot_height)
```

## Time (day number) of peak incidence by Cgq multiplier

```{r}
# Print scatter plot
plot_title <- paste0("Time (day number) of peak incidence by Cgq multiplier, based on ", nrow(outcomes.summary.df)," scenarios")
x_label <- "Cgq multiplier"
ggplotly(ggplot(outcomes.summary.df, aes(x = Cgq.multiplier, y = maxI.time)) +
    geom_point(aes(color = scenario), size = point_size) +
    ggtitle(plot_title) +
    xlab(x_label) +
    ylab(y_label) +
    theme_minimal() +
    theme(
       plot.title = element_text(size = element_text_size),
       axis.title.x = element_text(size = element_text_size),
       axis.title.y = element_text(size = element_text_size),
       legend.text = element_text(size = element_text_size),
       legend.title = element_blank()
  ), width = plot_width, height = plot_height)
```

## Time (day number) of peak incidence by lambda multiplier

```{r}
# Print scatter plot
plot_title <- paste0("Time (day number) of peak incidence by lambda multiplier, based on ", nrow(outcomes.summary.df)," scenarios")
x_label <- "Lambda multiplier"
ggplotly(ggplot(outcomes.summary.df, aes(x = lambda.multiplier, y = maxI.time)) +
    geom_point(aes(color = scenario), size = point_size) +
    ggtitle(plot_title) +
    xlab(x_label) +
    ylab(y_label) +
    theme_minimal() +
    theme(
       plot.title = element_text(size = element_text_size),
       axis.title.x = element_text(size = element_text_size),
       axis.title.y = element_text(size = element_text_size),
       legend.text = element_text(size = element_text_size),
       legend.title = element_blank()
  ), width = plot_width, height = plot_height)
```

## Time (day number) of peak incidence by beta multiplier

```{r}
# Print scatter plot
plot_title <- paste0("Time (day number) of peak incidence by beta multiplier, based on ", nrow(outcomes.summary.df)," scenarios")
x_label <- "Beta multiplier"
ggplotly(ggplot(outcomes.summary.df, aes(x = beta.multiplier, y = maxI.time)) +
    geom_point(aes(color = scenario), size = point_size) +
    ggtitle(plot_title) +
    xlab(x_label) +
    ylab(y_label) +
    theme_minimal() +
    theme(
       plot.title = element_text(size = element_text_size),
       axis.title.x = element_text(size = element_text_size),
       axis.title.y = element_text(size = element_text_size),
       legend.text = element_text(size = element_text_size),
       legend.title = element_blank()
  ), width = plot_width, height = plot_height)
```

## Time (day number) of peak incidence by sigma multiplier

```{r}
# Print scatter plot
plot_title <- paste0("Time (day number) of peak incidence by sigma multiplier, based on ", nrow(outcomes.summary.df)," scenarios")
x_label <- "Sigma multiplier"
ggplotly(ggplot(outcomes.summary.df, aes(x = sigma.multiplier, y = maxI.time)) +
    geom_point(aes(color = scenario), size = point_size) +
    ggtitle(plot_title) +
    xlab(x_label) +
    ylab(y_label) +
    theme_minimal() +
    theme(
       plot.title = element_text(size = element_text_size),
       axis.title.x = element_text(size = element_text_size),
       axis.title.y = element_text(size = element_text_size),
       legend.text = element_text(size = element_text_size),
       legend.title = element_blank()
  ), width = plot_width, height = plot_height)
```

# Data table

```{r}
datatable(outcomes.summary.df %>% select(-c(etiquette)) %>% mutate(maxI = as.integer(maxI), Cgg.multiplier = round(Cgg.multiplier, 3), Cgq.multiplier = round(Cgq.multiplier, 3), lambda.multiplier = round(lambda.multiplier, 3), beta.multiplier = round(beta.multiplier, 3), sigma.multiplier = round(sigma.multiplier, 3)) %>% arrange(desc(maxI.time, maxI)), 
  extensions = c("Buttons", "Scroller"), 
  options = list(
    pageLength = 50, 
    dom = "Bfrtip", 
    buttons = c("colvis", "copy", "csv", "excel", "pdf"), 
    deferRender = TRUE, 
    searchDelay = 500,
    initComplete = JS(
      "function(settings, json) {",
      "$(this.api().table().header()).css({'background-color': '#fff', 'color': '#111'});",
      "}"
    ),
    columnDefs = list(
      list(visible = FALSE, targets = c())
    )
  ), 
  rownames = FALSE,
  escape = FALSE,
  editable = TRUE
)
```